---
title: "Monthly Report"
author: "Oisin Hodgins"
date: "20/09/2020"
output: 
  slidy_presentation:
    footer: "Econiq Monthly Report"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.height = 5, comment=NA)
```

# Introduction
```{r process_data, warning=FALSE, error=FALSE, message=FALSE}
library(RReport)
library(ggplot2)
library(formattable)
setwd("~/EconiqDemoData")
read_csv_monthly_report("ClientOnlyCoreDataCleaned.csv")
process_guided_data()
process_agent_data_calls()
process_agent_data_colours()
process_agent_data_duration()
```

- Press the "**k**" key now to allow interaction with tables, without changing the slide
- The "**b**" key will increase font size, while the "**s**" key decreases it
- The "**c**" key displays the *table of contents*

# General Overview (Calls and their outcomes) [1]
```{r overview_stats}
find_total()
```
Total Calls made this month: `r nrow(core_data)`
  
  `r guided_total` of which were Guided Conversations (`r round((guided_total)/nrow(core_data),3)`%)   
  `r referral_total` of which were Referrals  (`r round((referral_total)/nrow(core_data),3)`%)    
  `r sale_total` of which were Sales  (`r round((sale_total)/nrow(core_data),3)`%)   
  
Average duration: `r mean(core_data$duration)%/%60` minutes, `r signif(mean(core_data$duration)%%60,2)` seconds

A total of `r nrow(total_customers)` customers were served, with `r sum(core_data$newCustomer)` being new customers.

# General Overview (Call outcome visualised) [2] {.smaller}
```{r outcome_plot, warning=FALSE, error=FALSE}
ggplot(core_data, aes(x = reorder(outcome, outcome, function(x)-length(x)))) +
    geom_histogram(stat = "count", fill = "pink") +
    theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
    labs(x = "Call Outcome", y = "Number of Calls")
```

# General Overview (Call duration visualised) [3] {.smaller}
```{r duration_hist, warning=FALSE, error=FALSE}
ggplot(core_data, aes(x=duration)) +
  geom_histogram(binwidth = 5, fill = "#9999CC") +
  theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust=1)) +
  labs(title = "Histogram of Call Durations", 
       x = "Call Duration", y = "Number of Calls")
```

# Agent Performance (Overview of Method) [1]

**How do our agents rank against each other this period?**

- We have ranked agents from best to worst on a number of different criteria, and combined all these metrics to give the overall agent performance.
  - The following metrics are directly proportional to performance
    - **Total calls**
    - The percentage of **Sales**, **Referrals** and **Guided Conversations**  which make up these calls
    - The **success rate** of an agent's **Guided Conversations**
    - The average number of **red clicks** an agent made in their calls
    
  - The following metrics are inversely proportional to performance
    - The average handling time (**AHT**) of an agents calls in the **other** category
  
  - The following metrics give the best score when they are close to the mean
    - The average handling time (**AHT**) of an agents calls not in the *other* category
    - The average number of **blue**, **green** and **purple** clicks in a call (note: these are ranked against the average clicks in a successful call)  
      
- These metrics are then standardized and normalized, meaning all values will lie between [0,1] with 0 being the worst recorded value and 1 being the best recorded value. The values are distributed based off the number of standard deviations they lie from the mean.

# Agent Performance (Heat Table) [2] {.smaller} 

```{r heat_table, warning=FALSE,message=FALSE}
agent_performance_analysis()
display_agent_performance_table()
```

# Agent Performance (Agent performance score) [3]

```{r agent_performance_plot}
ggplot(agent_kpi_analysis, aes(x = reorder(username,-agent_performance), 
                               y = agent_performance)) +
  geom_bar(stat = 'identity', fill = '#50B4E9') +
  theme(axis.text.x = element_text(angle = 90, vjust = 0, hjust=1)) +
  labs(title = "Agents ranked by their performance score", 
       x = "Agent Username", y = "Agent Performance score")
```

# Agent Performance (Calls) [4]

```{r call_plot}
ggplot(core_data, aes(x = reorder(username, username, function(x)-length(x)),fill = outcome)) +
    geom_bar() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0, hjust=1)) +
    labs(title = "Agents Ranked by Total Calls"
               , x = "Agent Username", y = "Number of Calls")
```

# Agent Performance (Sales) [5]

```{r sale_plot}
ggplot(agent_data, aes(x = reorder(username,-sale_percent), y = sale_percent)) +
    geom_bar(stat = 'identity', fill = '#56B4E9') +
    theme(axis.text.x = element_text(angle = 90, vjust = 0, hjust=1)) +
    labs(title = "Percentage of Sales", x = "Agent Username", y = "Sales")
```

# Agent Performance (Referrals) [6]

```{r ref_plot}
ggplot(agent_data, aes(x = reorder(username,-ref_percent), y = ref_percent)) +
    geom_bar(stat = 'identity', fill = '#009E73') +
    theme(axis.text.x = element_text(angle = 90, vjust = 0, hjust=1)) +
    labs(title = "Percentage of Referrals", x = "Agent Username", y = "Referrals")
```

# Agent Performance (Guided Conversations) [7]

```{r guided_plot}
ggplot(agent_data, aes(x = reorder(username,-guided_percent), y = guided_percent)) +
    geom_bar(stat = 'identity', fill = '#CC79A7') +
    theme(axis.text.x = element_text(angle = 90, vjust = 0, hjust=1)) +
    labs(title = "Percentage of Guided Conversations", x = "Agent Username", y = "Guided Conversations")
```


# Agent Performance (AHT) [8]

```{r AHT_plot}
ggplot(agent_data, aes(x = reorder(username,-AHT), y = AHT)) +
    geom_bar(stat = 'identity', fill = '#E69F00') +
    theme(axis.text.x = element_text(angle = 90, vjust = 0, hjust=1)) +
    labs(title = "Agents ranked by AHT, where outcome is not 'other'", x = "Agent Username", y = "Average Handling Time")
```

# Agent Performance (AHT, where outcome = other) [9]

```{r AHT_other_plot}
ggplot(agent_data, aes(x = reorder(username,-AHT_other), y = AHT_other)) +
    geom_bar(stat = 'identity', fill = '#009E73') +
    theme(axis.text.x = element_text(angle = 90, vjust = 0, hjust=1)) +
    labs(title = "Agents ranked by AHT, where the outcome is 'other'", x = "Agent Username", y = "Average Handling Time")
```

# Guided Conversation Analysis (Overview of Method) [1]

**What metrics best predict if a Guided Conversation will be successful or not?**

- We aim to answer this question through multivariate logistic regression
  - We will rank the predictors in order of significance, highlighting those which we can conclude are statistically significant
    - This is done in part through Wald tests and also a Chi-Square test 
    
# Guided Conversation Analysis (Agent choice) [2]

```{r chi_test, echo=FALSE, warning=FALSE, error=FALSE}
agent_guided_success_Chi_Square_test()
```

# Guided Conversation Analysis (Agent Plot) [3]

```{r chi_plot}
ggplot(plot_data, aes(x=reorder(username, username, function(x)-length(x)),fill = success)) +
    geom_bar(position = position_dodge(width=1)) +
    theme(plot.title = element_text(size=10,face="bold")) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0, hjust=1, size=4)) +
    theme(legend.title = element_text(size = 8), legend.text = element_text(size=6)) +
    scale_fill_discrete(name="Success") +
    labs(title = "Agents vs. Guided Conversations,\n grouped by success"
         , x = "Agent username", y = "Tally")
```

# Guided Conversation Analysis (Regression) [4]

```{r guided_reg, warning=FALSE, error=FALSE}
logit_reg_guided()
```

